---
title: "ENVS-193DS_winter-2026_final"
author: "Leah Pettway"
date: "03/16/26"
format: html
---

Github-repo-link: https://github.com/leahlamarre-ship-it/ENVS-193DS_winter-2026_final

```{r}
#| label: Set-up
#| message: false

library(tidyverse)
library(janitor)
library(here)
library(readxl)
library(dplyr)
library(readr)

kelp <- read_csv("/Users/leahpettway/ENVS-193DS/github/ENVS-193DS_final/ENVS-193DS_winter-2026_final/data/Annual_Kelp_All_Years_20250903.csv")

mopl <- read_csv("/Users/leahpettway/ENVS-193DS/github/ENVS-193DS_final/ENVS-193DS_winter-2026_final/data/MOPL_nest-site_selection_Duchardt_et_al._2019.csv")

my_data <- read_csv("/Users/leahpettway/ENVS-193DS/github/ENVS-193DS_final/ENVS-193DS_winter-2026_final/data/Personal_data.csv")

```

## Problem 1. Research writing

### a. Transparent statistical methods

### b. Figure needed

### c. Suggestions for rewriting

### d. Interpretation

## Problem 2. Data visualization

### a. Cleaning and summarizing

```{r}
#| label: clean and wrangle kelp data


```

### b. Understanding the data

### c. Visualize the data

```{r}
#| label: Recreated visualization


```

### d. Interpretation

## Problem 3. Data analysis

### a. Response variable

### b. Purpose of study

### c. Table of models

```{r}
#| label: Tables





```

### d. Run the models

```{r}
#| label: clean and wrangle mopl data



```

```{r}
#| label: run models




```

### e. Select the best model

### f. Check the diagnostics

```{r}
#| label: Checking diagnostics






```

### g. Visualize the model predictions

```{r}
#| label: Visualize models





```


### h. Write a caption for your figure

### i. Calculate model predictions

```{r}
#| label: Calculate predictions






```

### j. Interpret your results

## Problem 4. Affective and exploratory visualizations

### a. Comparing visualizations

### b. Designing an analysis

### c. Check any assumptions and run your analysis

### Assumptions

```{r}
#| label: Checking assumptions

```

### analysis

```{r}
#| label: Run the analysis

```

### effect size

```{r}
#| label: calc effect size



```

### d. Create a visualization

```{r}
#| label: Visualization




```

### e. Write a caption

### f. Write about your results

### g. Sharing your affective visualization
















































